% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Gautam }{Kumar }           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{Contact}
69,Wolfenden Hall
IIEST,Shibpur
~
\textbf{Mobile no:}
+91 9903199342
~
\textbf{Email:}
gautam.kriiest@gmail.com
%
\section{Languages}
English\\
Hindi
%
\section{Programming
   Languages}
C\\
Python
%
\section{Skills}
SQL\\Linux\\Excel\\Word\\Android studio\\Powerpoint\\Raspberry pi
%
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2016--2020}
{B.Tech {\normalfont in Information Technology( 7.07 CGPA)}}
{IIEST,Shibpur}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2015}
{Senior Secondary Education {\normalfont PCM (77.80\%)}}
{M.L.T College,Saharsa}
{\vspace{-0.3cm}}
\entry
{2013}
{Secondary Education  {\normalfont Science (10 CGPA)}}
{St. Joseph Public School,Dalsingsarai}
{}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{ Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{May-Jul 2018}
{A Smart Gym Interactive System Using Sensors }
{IIT BHU}
{The primary objective behind our project is to help a person train in GYM without the help of a trainer using an ML model. We are developing an ML model that will learn the correct technique of GYM exercises by trainers using the data collected from them by various sensors.}
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Dec-2017}
{Performance Analysis Of Line Codes In Digital Data Transmission}
{IIEST,Shibpur}
{Worked on various Line Coding Schemes Under \textbf{Prof. Santi Prasad Maiti, Department of Information Technology,IIEST Shibpur} }
{\vspace{-0.3cm}}
\end{entrylist}



%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------

\section{Position Of Responsibility}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Publicity Head at INSTRUO 2018}
{IIEST,Shibpur}
{College Technical Fest.}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{}
{Publicty/Sponsorship Associates at INSTRUO 2017}
{IIEST,Shibpur}
{College Technical Fest.}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Core Team Member,Scintillation 2K17 }
{IIEST,Shibpur}
{Organized by Entrepreneurship Development Cell of IIEST,Shibpur}

\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Volunteer at Indian Road Safety Campaign,IIEST Shibpur Chapter }
{IIEST,Shibpur}
{Safe Road Mini-Marathon, for the cause of Social Services.}

\end{entrylist}\\\\\

%----------------------------------------------------------------------------------------
%	INTERNSHIP SECTION
%----------------------------------------------------------------------------------------

\section{Internships}
  \vspace{-0.3cm}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{ Research Intern at IIT,BHU}
{}
{Worked on Machine learning Models and IoT Under\textbf{ Dr. Hariprabhat Gupta,Department of Computer Scince,IIT BHU} }
\end{entrylist}\

\



%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%-----------------------------------------------------------------------

\section{Skills}
  \vspace{-0.3cm}
\begin{entrylist}
%------------------------------------------------
\entry
  {}
  {Good Management skills}
  {}
  {\jobtitle{}\ Management Skills which require in company}
%------------------------------------------------
\entry
  {}
  {Programming Ability }
  {}
  {\jobtitle{}\ Good programming skills in C and Python.}
  
  \entry
  {}
  {Quick Learning Capability}
  {}
 {\jobtitle{}\ }
  
  \entry
  {}
  {Good in Communication }
  {}
  {\jobtitle{}\ }
     \entry
  {}
  {Position Of Responsibility }
  {}
  {\jobtitle{}\-Publicity Head at INSTRUO 2018,IIEST Shibpur }
%------------------------------------------------
%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}

\begin{entrylist}
\entry
{}
{Attended 2nd INAE Youth Conclave}
{IIT,KGP}
{Conducted at Indian Institute of Technology, Kharagpur}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Workshop on Android App Development}
{IIEST,Shibpur}
{Conducted by INSTRUO 2K17 at IIEST,Shibpur}

\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Core Java With Android}
{Patna}
{Conducted at HPES Summer training Nodal Center,Patna with \textbf{oracle Certification}\\Certificate ID: 50412393}

\end{entrylist}\\\\\

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Hobby SECTION
%----------------------------------------------------------------------------------------
\section{Career Interests}
    \vspace{-0.2cm}
    
\begin{entrylist}

\entry
{}
{Internet Of Things\\
Business Development\\
Machine Learning\\
Network Security\\
SQL.
}
{}
{Looking Forward to work on these fields.}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	Hobby SECTION
%----------------------------------------------------------------------------------------




\section{Hobbies}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
  {}
  {Learn about new  technology }
  {}
  {\jobtitle{}\ Learn about the latest technology which helpful in company and Improve my
     Skills as well.}
  

  \entry
  {}
  {Sports }
  {}
  {\jobtitle{}\ Like Badminton,Table Tennis,Chess and Cricket. }
  
 
%------------------------------------------------
%------------------------------------------------

\end{entrylist}


\end{document}